\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

%\pagenumbering{arabic}
\clearpage
\thispagestyle{empty}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[5]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\\ \smallskip
			{#5}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Oren Shoham}{https://github.com/oshoham}{http://www.linkedin.com/pub/oren-shoham/66/1b4/b37}{oshoham@oberlin.edu}{(713) 408-9422}

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{Oberlin College}{} \hfill \emph{Fall 2010 - Spring 2014 (Expected Graduation Date)}{} \\
	B.A. in Computer Science \\
	GPA --- Overall: 3.65/ Computer Science: 3.75 \\
	\medskip
	\emph{{\bf Relevant Courses:}} Data Structures, Programming Abstractions, Algorithms, Discrete Mathematics, Game Design, Artificial Intelligence, Theory of Computation, Computer Organization, Systems Programming, Information Theory, Cryptology, Human Computer Interaction
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

\begin{body}
	\vspace{14pt}
	\emph{\textbf{Programming:}}{} Java, Python, C, Ruby on Rails, HTML, CSS/Sass, Javascript, C\#, Scheme, \LaTeX \\
	\medskip
	\emph{\textbf{Tools:}}{} Windows, Mac OS X, Unix, Unity 3D, Vim, Git, R, SQL \\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{Awards and Honors}

\begin{body}
	\vspace{14pt}
	\textbf{Nu Rho Psi}: National Honor Society in Neuroscience, Oberlin College \hfill{} \emph{Spring 2013 - Present}\\
	\smallskip
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Experience}

\begin{body}
	\vspace{14pt}

	\textbf{Co-founder/Developer}, \emph{LabRats (Startup Project)} \hfill \emph{Fall 2013}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Developed a note-taking application intended to allow scientists to digitize their lab notebooks and easily manage, share, and review experimental data.
		\item Worked with a team of 4 in a full-stack development role using Rails, Backbone.js, RSpec, and Jasmine.
		\item Gained experience with the technical and business challenges of getting a startup off the ground.
		\item Received an honorable mention from the 2014 Oberlin College Launch U Startup Accelerator Program.
	\end{itemize}

	\textbf{OWLS Leader}, \emph{Oberlin College} \hfill \emph{Fall 2013}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Ran bi-weekly Oberlin Workshop and Learning Sessions (OWLS) for the Fall 2013 Introduction to Algorithms course along with a co-instructor.
		\item Facilitated peer-to-peer learning sessions in which students worked collaboratively to improve their understanding of algorithms topics such as greedy algorithms, dynamic programming, network flows, and computational complexity.
	\end{itemize}

	\textbf{Web Development}, \emph{oprestissimo.com/Oberlin College} \hfill \emph{Summer 2013}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Worked as part of the development team for Prestissimo, a student-created Ruby on Rails search engine for the  Oberlin College course catalog.
		\item Added several features to Prestissimo's front-end using HTML, CSS/Sass, Javascript, and Ruby.
		\item Wrote shell scripts and Rake tasks for updating and maintaining the site's MySQL database.
		\item Improved the functionality and design of the search interface.
	\end{itemize}

	\textbf{Neuroscience Research}, \emph{Oberlin College} \hfill \emph{Spring 2013 - Present}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Worked in Prof. Michael Loose's research lab studying decision making in two-choice gambling tasks using EEG data and mathematical modeling.
		\item Participated in the deisgn and execution of several behavioral experiments.
		\item Analyzed behavioral data using a version of the Drift Diffusion Model and an artificial neural network.
	\end{itemize}

	%\textbf {Independent Research}, \emph{Oberlin College} \hfill \emph{January 2013}\\
	%\vspace*{-4pt}
	%\begin{itemize} \itemsep -0pt
	%	\item Studied techniques for evolving artificial neural networks to control agents that could %perform "minimally cognitive tasks" using genetic algorithms.
	%	\item Wrote implementations of several neural network models and genetic algorithms in %Python.
	%\end{itemize}

	\textbf{Game Design}, \emph{Oberlin College} \hfill \emph{Fall 2012}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Created an action/puzzle game called R.G.B. in Unity3D as part of a 4-person team.
		\item Implemented AI behavior, in-game physics (e.g. collision detection), and user interfaces using C\#.
	\end{itemize}

	\textbf{Computer Science Department Grader}, \emph{Oberlin College} \hfill \emph{Fall 2012}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Graded for Introduction to Algorithms (CS 280), which covers topics such as greedy algorithms, dynamic programming, network flows, computational complexity, and approximation algorithms.
		\item Analyzed 20+ students' algorithms and proofs, providing constructive, detailed feedback regarding algorithm design and proof techniques.
	\end{itemize}
\end{body}

\end{document}