\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[5]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4} \\ \smallskip
			{#5}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}
\pagenumbering{gobble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Oren Shoham}{https://github.com/oshoham}{315 Troutman St., Brooklyn, NY 11237}{orenavrahamshoham@gmail.com}{(713) 408-9422}

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{Oberlin College}{} \hfill \emph{September 2010 - May 2014}{} \\
	B.A. in Computer Science \\
	GPA --- Overall: 3.7/ Computer Science: 3.75 \\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical Skills
\header{Technical Skills}

\begin{body}
	\vspace{14pt}
	\emph{\textbf{Languages:}}{} 
		\begin{itemize} \itemsep -0pt  % reduce space between items
			\item \textbf{Most Familiar:} Python, Javascript, Ruby, HTML/CSS
			\item \textbf{Have Used for Fun or School:} C, Java, C\#, Bash, Scheme, \LaTeX \\
		\end{itemize}
	\medskip
	\emph{\textbf{Frameworks:}}{} Django, Rails, Backbone, Ember \\
	\medskip
	\emph{\textbf{Databases:}}{} PostgreSQL, MongoDB \\
	\medskip
	\emph{\textbf{Tools:}}{} Unix, Vim/Sublime Text, Git, Unity3D \\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{Awards and Honors}

\begin{body}
	\vspace{14pt}
	\textbf{Nu Rho Psi}: National Honor Society in Neuroscience, Oberlin College \hfill{} \emph{Spring 2013 - Present}\\
	\smallskip
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Experience}

\begin{body}
	\vspace{14pt}

	\textbf{Software Developer}, \emph{DecisionDesk} \hfill \emph{July 2014 - Present}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Educational technology SaaS startup creating applicant management software for higher education institutions.
		\item Full-stack responsibilities using Rails, Ember, and PostgreSQL, as well as Django, Backbone, and MongoDB (for a legacy product).
		\item Built single-page web apps for applying to schools, reviewing applications, and managing the admissions process.
		\item Implemented a REST API for managing application data.
		\item Gained familiarity with testing tools (RSpec, pytest) and TDD, devops tools (Chef, Vagrant) and infrastructure best practices, and AWS (S3, EC2, IAM).
	\end{itemize}

	\textbf{Algorithms TA}, \emph{Oberlin College CS Department} \hfill \emph{Fall 2013}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Ran bi-weekly Oberlin Workshop and Learning Sessions (OWLS) for the Fall 2013 Introduction to Algorithms course along with a co-instructor.
		\item Facilitated peer-to-peer learning sessions in which students worked collaboratively to improve their understanding of algorithms topics such as greedy algorithms, dynamic programming, network flows, and computational complexity.
	\end{itemize}

	\textbf{Software Developer}, \emph{Prestissimo (oprestissimo.com)} \hfill \emph{June 2013 - August 2013}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Student-created search engine for the  Oberlin College course catalog.
		\item Full-stack responsibilities using Rails, Bootstrap, and MySQL.
		\item Improved the speed of course searching by rewriting the Javascript code responsible for populating the UI with the results of database queries.
		\item Updated the search interface and the structure of the site's database to account for changes in Oberlin College's course credit system.
		\item Wrote shell scripts and Rake tasks for parsing raw course data received from Oberlin College.
	\end{itemize}

	\textbf{Neuroscience Researcher}, \emph{Oberlin College Neuroscience Department} \hfill \emph{February 2013 - May 2014}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Worked in Prof. Michael Loose's research lab studying decision making in two-choice gambling tasks using EEG data and mathematical modeling.
		\item Participated in the design and execution of several behavioral experiments.
		\item Analyzed behavioral data using an artificial neural network.
	\end{itemize}
\end{body}

\end{document}